### 2017-08-03 README.Rmd
small commit for testing
update package description

Infer: a grammar for statistical inference

@@

The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.

@@

These examples assume that `mtcars` has been overwritten so that the variables
`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s:

>>>>

Infer: An R package for tidyverse-friendly statistical inference

@@

The objective of this package is to perform inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.

@@

These examples assume that `mtcars` has been overwritten so that the variables
`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.
